---
title: "easydta: single-test DTA meta-analysis (anti-CCP2)"
output: html_document
---

```{r packages}
if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman")
}
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}
if (!requireNamespace("easydta", quietly = TRUE)) {
  remotes::install_github("vanioljantunes/easydta")
}
pacman::p_load(easydta)   # attaches ggplot2 too (easydta Depends on it)
```

```{r load_data}
# Cochrane Handbook chapter 10 / Appendix 14 anti-CCP dataset
# (Nishimura et al. systematic review).  Bundled single-arm subset; the
# `test` column carries the assay generation (CCP1 vs CCP2).  For the
# single-test demo we use the larger CCP2 arm.
data(anti_ccp2)
d <- anti_ccp2
head(d)
```

```{r fit}
fit <- dta_fit_single(d, wide = TRUE,
                      tp = "TP", fp = "FP", fn = "FN", tn = "TN",
                      studlab = "studlab")
print(fit)
```

## Forest plot

`dta_forest()` renders a coupled sensitivity / specificity forest as a
single composite. Reading the panels left to right:

1. `studlab` and the raw `TP / FN / TN / FP` counts (the **Summary** row
   is bold and shows the column totals);
2. per-study sensitivity point estimate with exact (Clopper-Pearson) 95%
   CI and the bivariate-GLMM summary diamond, with a dashed vertical
   reference line through the diamond centre;
3. the numeric sensitivity `est (lci-uci)` column;
4. the same pair of panels for specificity.

The bivariate Zhou-Dendukuri I² is split across three small italic
annotations placed directly under each summary block: `I²(biv)` under
the Summary label, `I²(sens)` under the sens diamond, `I²(spec)` under
the spec diamond. A solid x-axis line with ticks sits just below the
diamond row on each CI panel; row backgrounds are zebra-shaded
continuously across all five panels.

```{r save_forest}
png("forest_ccp2.png", width = 1400, height = 1000, res = 150)
dta_forest(fit)
dev.off()
```

```{r save_sroc}
png("sroc_ccp2.png", width = 1200, height = 1000, res = 150)
p <- dta_sroc(fit, test = "anti-CCP2",
              outcome = "rheumatoid arthritis",
              population = "adults")
print(p)
dev.off()
```

## Deeks funnel plot + asymmetry test

`dta_funnel()` renders the Cochrane-recommended publication-bias
diagnostic for DTA reviews (Handbook v2.0 ch. 10.6.4; Deeks, Macaskill
& Irwig 2005). The funnel plots `ln(DOR)` against `1/sqrt(ESS)` (the
y-axis is reversed so larger studies sit at the top), and the table
below reports the weighted-regression Deeks test for funnel asymmetry
(`lm(lnDOR ~ 1/sqrt(ESS), weights = ESS)` -- the slope p-value is the
Deeks p; p < 0.05 suggests asymmetry consistent with publication bias).

```{r save_funnel}
png("funnel_ccp2.png", width = 1200, height = 1100, res = 150)
dta_funnel(fit,
           test       = "anti-CCP2",
           outcome    = "rheumatoid arthritis",
           population = "adults")
dev.off()
```
